---
title: "Lab 2"
author: "Gabriele Hayden"
date: "October 9, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
# Ignore this first code chunk for now.

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

1. Run the following code to 
  (a) install the {nlme} and {janitor} packages
  (b) load the packages along with the tidyverse, and
  (c) access and quickly prep some data (from the {nmle} package) for plotting.

```{r data-download, eval = FALSE, echo = TRUE}
install.packages(c("nlme", "janitor")) # (a)
library(nlme) # (b)
library(janitor) # (b)
library(tidyverse) # (b)

# (c) below
pd <- Oxboys %>% # start with the Oxboys data
  clean_names() %>% # function from the janitor package to clean variable names
  mutate(subject = factor(subject), # make subject a factor
         occasion = factor(occasion)) %>% # make occasion a factor
  filter(subject == "10" | subject == "4" | subject == "7") %>% # filter for subjects "10", "4", and "7"
  as_tibble() # make the data.frame a tibble
```

1. Reproduce the following two plots, using the *pd* data. You can use whatever theme you want (I used `r theme_minimal()`), but all else should be the same. 

```{r plots1, message = FALSE, warning = FALSE}
# put script for Plot 1 here
ggplot(pd, aes(age, height)) +
  geom_line() +
  facet_wrap(~subject)

# put script for Plot 2 here
p <- ggplot() +
  geom_line(filter(pd, subject == 10), aes(x = age, y = height), color = "purple") +
  xlab("Age") +
  ylab("Height")


```

\newpage

2. Use the *mtcars* dataset from base R to replicate the following plots. (Just type *mtcars* into the console to see the dataset).

```{r plots2}
# put script for Plot 3 here



# put script for Plot 4 here



# put script for Plot 5 here



# put script for Plot 6 here



```

\newpage

3. Use the *Orange* dataset, also part of base R, to replicate the following plots.
   
```{r orange-plots}
# put script for Plot 7 here



# put script for last plot here



```

When you knit (click the yarn ball icon at the top), it should render as a .pdf. Turning in a .pdf or a .html are both acceptable. Upload the final rendered document to Canvas. (Be sure to put your name up top in the YAML.)